Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-05-22 tex/ms.tex
better figures for older cluster

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
subtraction happened.  We got data which were uncalibrated and data
which had been approximately spectrophotometrically calibrated using
an average for the night (MORE HERE). Figure \ref{fig:data} shows the
calibrated and uncalibratred spectra for each cluster.  Discuss S/N,
sky subtraction, calibration.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt(2\pi)} e^{-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2}}
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_e \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
and redshift $z$,
and amplitudes of the $N_l$ nebular and interstellar emission lines
$a_i$.

@@

Discuss degeneracies, etc.  Apparently we get really nice
redshift/velocity constraints for free.

Next, we infer the parameters of the spectrum of the same cluster
\emph{without} spectrophotometric calibration.

Then, we show select marginalized or joint PDFs for each cluster
calibrated/uncalibrated, to assess consistency.

Finally, we have fun playing with the number of photometric bands and the S/N.

>>>>

The data we use to test our method consists of optical spectroscopy of
XX stellar clusters in M31 for which YY-band HST photometric data
exist.  The optical spectra were obtained using the fiber-fed
Hectoscpec intrument on MMT by \citet{caldwell}.  The wavelength range
of the spectra is $3700-7200 \AA$. The instrumental resolution is
$\sim 5\AA$ across the optical range \citep{fabricant13}.  Sky
subtraction happened. The data were approximately
spectrophotometrically calibrated using an average calibration vector
the night constructed from.... (MORE HERE). Figure \ref{fig:data}
shows the spectra before and after calibration for each cluster.
Discuss S/N, sky subtraction.

\subsection{Star Cluster Model}
We model the stellar cluster as a single age SSP. The spectrum of a
star cluster under this assumption is given by
\begin{eqnarray}\displaystyle\label{eq:MeanModel} 
\mu(\theta, \lambda_o) & = &
\frac{m_*}{4\pi d_L^2(1+z)} \, G(\lambda,\sigma) \otimes 
S(\lambda, t, Z , \beta) \, e^ {-k_\lambda\tau_V}  + \\
& & \sum_{i=0}^{N_l} \frac{a_i}{\sigma_e\sqrt{2\pi}} \exp(-\frac{(\lambda - \lambda_i)^2}{2\sigma_e^2})
\nonumber \\ 
\lambda_o & = & (1+z)\,\lambda 
\\
\theta & \equiv & \left[ m_*, t, Z, \tau_V, \sigma_v, z, d_L, \beta,
  \{a_i\}_{i=0}^{N_l}, \sigma_e \right]
\quad ,
\end{eqnarray} where the parameters $\theta$ include 
the stellar mass $m_*$, 
effective optical depth to dust in the $V$-band $\tau_V$,
velocity dispersion or instrumental resolution $\sigma$, 
luminosity distance $d_L$, 
redshift $z$,
and amplitudes of the $N_l$ nebular and interstellar emission lines
$a_i$.

@@

BDJ: Discuss degeneracies, etc.  Apparently we get really nice
redshift/velocity constraints for free.

BDJ: Next, we infer the parameters of the spectrum of the same cluster
\emph{without} spectrophotometric calibration.

BDJ: Then, we show select marginalized or joint PDFs for each cluster
calibrated/uncalibrated, to assess consistency.

BDJ: Finally, we have fun playing with the number of photometric bands
and the S/N.
